Fourmile Calibrations

### 2023-01-24 calibration_output.Rmd
ready for meeting. Still need to figure out dates of percentiles and SWE comparison for Niwot

mo_rmse <- ensem %>%
  ungroup() %>%
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = rmse(grid_ensemble, obs),
            statn_ensemble = rmse(statn_ensemble, obs),
            all_ensemble = rmse(all_ensemble, obs),
            grid_all = rmse(grid_all, obs),
            statn_all = rmse(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

###
# quantile_cal <- function(data, prob) {
#   data %>%
#     dplyr::group_by(cal_run, year) %>%
#     mutate(quantile = paste0(prob),
#            value = quantile(cumsum, prob)) %>%
#     filter(cumsum >= value) %>%
#     filter(date == min(date))
#   }
# 
# quantiles <- c(0.25, 0.5, 0.75)
# 
# quants <- quantiles %>% 
#   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
#   bind_rows()
####

@@

perc_plots <- lapply(name, perc_plots)

htmltools::tagList(plot_perc_ensem)

@@

##tmean 
tmean <- catchment %>%
  group_by(year, site) %>%
  summarize(tmean = mean(tmean)) %>%
  ggplot(aes(x = year, y=tmean, color = site)) +
  geom_point(size=3) +
  ggtitle('Average temp by year')

@@

>>>>

mo_rmse <- ensem %>%
  ungroup() %>%
  drop_na() %>% 
  mutate(month = month(date)) %>%
  group_by(month) %>%
  summarize(grid_ensemble = rmse(grid_ensemble, obs),
            statn_ensemble = rmse(statn_ensemble, obs),
            all_ensemble = rmse(all_ensemble, obs),
            grid_all = rmse(grid_all, obs),
            statn_all = rmse(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 4)

@@

###
quantile_cal <- function(data, prob) {
  data %>%
    dplyr::group_by(cal_run, year) %>%
    mutate(quantile = paste0(prob),
           value = quantile(cumsum, prob)) %>%
    group_by(cal_run, year, quantile) %>% 
    filter(cumsum >= value) %>%
    filter(date == min(date))
  }

quantiles <- c(0.25, 0.5, 0.75)

quants <- quantiles %>%
  map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
  bind_rows()
####

@@

perc_plots <- lapply(name, plot_perc_ensem)

htmltools::tagList(perc_plots)

@@

## tmean 
tmean <- catchment %>%
  group_by(year, site) %>%
  summarize(tmean = mean(tmean)) %>%
  ggplot(aes(x = year, y=tmean, color = site)) +
  geom_point(size=3) +
  ggtitle('Average temp by year')

@@

## Niwot

### SWE

-Look at SWE dataframe as a group

```{r niwot, echo = F}
library(snotelr)

niwot_snotel <- snotel_download(site_id = 663, internal = T)

niwot_snotel <- niwot_snotel %>%
  select(date, snow_water_equivalent, precipitation) %>%
  mutate(date = as.Date(date)) %>%
  rename(swe_mm_snotel = snow_water_equivalent,
         precip_mm_snotel = precipitation) %>%
  #mutate(swe_mm_snotel = swe_mm_snotel*25.4,
         #precip_mm_snotel = precip_mm_snotel*25.4) %>%
  filter(date > '2010-12-31' & date < '2020-10-01')

hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrugrid = precip_mm,
         swe_mm_hrugrid = swe_mm)

hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrustatn = precip_mm,
         swe_mm_hrustatn = swe_mm)

niwot <- niwot_snotel %>%
  left_join(hru7_grid, by = 'date') %>%
  left_join(hru7_statn, by = 'date')

#look at swe -- ****** ask about this
niwot_swe <- niwot %>%
  dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn) %>%
  mutate(swe_mm_snotel2 = swe_mm_snotel - lag(swe_mm_snotel))

kable(niwot_swe) %>%
  kable_styling(full_width = F) %>% 
  scroll_box(width = "100%", height = "500px")

# niwot_swe <- niwot_swe %>% 
#   pivot_longer(!date, names_to = 'source', values_to = 'swe_mm')

### ET

```{r ET, echo = F}

niwot_et <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/Niwot_daily_et.csv') %>%
  filter(year > 2010) %>%
  mutate(date = make_date(year = year, month = month, day = day)) %>%
  select(date, et) %>%
  rename(et_niwot = et)

hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  select(date, AET_mm) %>%
  rename(et_hru7grid = AET_mm)

hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  select(date, AET_mm) %>%
  rename(et_hru7statn = AET_mm)

niwot_et_compare <- niwot_et %>%
  left_join(hru7_grid, by = 'date') %>%
  left_join(hru7_statn, by = 'date') %>%
  mutate(year = year(date)) %>%
  filter(year < 2021) %>% 
  pivot_longer(!c(date, year), names_to= 'source', values_to = 'et_mm') %>%
  mutate(year = as.factor(year))

#plot ET by year
plot_ET <- function(calyear) {
  {niwot_et_compare %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = et_mm, color = source)) +
    geom_line(size=1) +
    ggtitle(calyear) +
    ylab('ET (mm/day)') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
    ggplotly()
}

name <- levels(niwot_et_compare$year)

ET_plots <- lapply(name, plot_ET)

htmltools::tagList(ET_plots)

ET_plots
